Supplemental Materials, Methods and Results

### 2021-04-29 supp.Rmd
Up to predators for model checking

 # Contrasts hypothesis tests, but use RVE 
                 result2 <- Wald_test(ConspicDisplayCC2, constraints = constrain_pairwise(c(2:9)), vcov="CR2", tidy = TRUE)
    result2$p_val_bonfer <- sapply(p.adjust(result1$p_val, "bonferroni"), function(x) p_value(x))

@@

# Fit model
ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population + BodyRegion +  
                             + Population:BodyRegion + (1|ID), data=Courtship)
anova(ConspicCourtshipAC)

ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population + BodyRegion + (1|ID), data=Courtship)
summary(ConspicCourtshipAC)
anova(ConspicCourtshipAC)

# Courtship - Chromatic dl

Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
ConspicCourtshipAC2 <- lmer(dL ~ PopBRInt + (1|ID), data=Courtship)
summary(glht(ConspicCourtshipAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                            "Hawaii.midflank - Kenya.midflank = 0", 
                                                            "Hawaii.topflank - Kenya.topflank = 0", 
                                                            "Hawaii.tailbase - Kenya.tailbase = 0" ))))

# Courtship - Chromatic dS
ConspicCourtshipCC <- lmer(dS ~ SVL + Population + BodyRegion + Background 
                           + Population:Background + Population:BodyRegion + (1|ID), data=Courtship)
Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
ConspicCourtshipCC2 <- lmer(dS ~ PopBRInt + (1|ID), data=Courtship)
summary(glht(ConspicCourtshipCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                            "Hawaii.midflank - Kenya.midflank = 0", 
                                                            "Hawaii.topflank - Kenya.topflank = 0", 
                                                            "Hawaii.tailbase - Kenya.tailbase = 0" ))))

@@

# Transformation, just in case residuals are non-normal they may help. Remember, models assume normality of residuals not normality of the data. None-normality could be driven by effects you wish to model. So, you need to account for these first.
Predator <- Predator %>% mutate(log_dS = log(dS),
                                log_dL = log(dL),
                                sqrt_dS = sqrt(dS),
                                sqrt_dL = sqrt(dL))

## Predator Model - Achromatic contrast (AC or dL)
## just this next section has Drew's code, which averages the backround (Leaf_B1, Leaf_B2, Leaf_T1, Leaf_T2, Stem1, Stem2) for each lizard body region measurement.
## This is the full model; however, we do not need background because the way the data is set up R is taking an average. See next model (background dropped)
PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion + Background 
                         + Predator:Background + Predator:BodyRegion + (1|ID), data=Predator)
anova(PredatorAC)

# Posthoc tests
Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorAC2 <- lmer(sqrt_dL ~ PopBRInt + (1|ID), data=Predator)
summary(glht(PredatorAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                    "Hawaii.midflank - Kenya.midflank = 0", 
                                                    "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))
## dropping background from model (it is still averaged)
# anova gives us significance of fixed effects
# ranova tests random effects (note: report just LRT and df)
# need the SD of residuals and random effects from summary (just report random effects)

>>>>

 # Contrasts hypothesis tests, but use RVE 
                 result2 <- Wald_test(ConspicDisplayCC2, constraints = constrain_pairwise(c(2:9)), vcov="CR2", tidy = TRUE)
    result2$p_val_bonfer <- sapply(p.adjust(result2$p_val, "bonferroni"), function(x) p_value(x))

@@

##########
## Achromatic Contrast - dL
##########
  # Fit model
    ConspicCourtshipAC <- lmer(dL ~ sc_SVL + Population + BodyRegion + Population:BodyRegion + (1|ID), data=Courtship)
    summary(ConspicCourtshipAC)
      anova(ConspicCourtshipAC)

  # Robust variance estimators (RVE). Mostly all consistent
             Courtship_subset <- Courtship %>% filter(!is.na(sc_SVL), !is.na(Population), !is.na(BodyRegion))
    robust_ConspicCourtshipAC <- coef_test(ConspicCourtshipAC, cluster = Courtship_subset$ID, vcov="CR2")

  # Refit model for contrasts
     Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
    ConspicCourtshipAC2 <- lmer(dL ~ -1 + sc_SVL + PopBRInt + (1|ID), data=Courtship)

  # Contrasts hypothesis tests, but use RVE 
                 result3 <- Wald_test(ConspicCourtshipAC2, constraints = constrain_pairwise(c(2:9)), vcov="CR2", tidy = TRUE)
    result3$p_val_bonfer <- sapply(p.adjust(result3$p_val, "bonferroni"), function(x) p_value(x))

##########
## Chromatic Contrast - dL
#########

    # Fit model
        ConspicCourtshipCC <- lmer(dS ~ sc_SVL + Population + BodyRegion + Population:BodyRegion + (1|ID), data=Courtship)

    # Robust variance estimators (RVE). Mostly all consistent
             Courtship_subset <- Courtship %>% filter(!is.na(sc_SVL), !is.na(Population), !is.na(BodyRegion))
    robust_ConspicCourtshipCC <- coef_test(ConspicCourtshipCC, cluster = Courtship_subset$ID, vcov="CR2")

    # Refit model to get the contrasts between coefficienst we want
     Courtship$PopBRInt <- interaction(Courtship$Population,Courtship$BodyRegion)
    ConspicCourtshipCC2 <- lmer(dS ~ -1 + sc_SVL + PopBRInt + (1|ID), data=Courtship)

    # Contrasts hypothesis tests, but use RVE 
                 result4 <- Wald_test(ConspicCourtshipCC2, constraints = constrain_pairwise(c(2:9)), vcov="CR2", tidy = TRUE)
    result4$p_val_bonfer <- sapply(p.adjust(result4$p_val, "bonferroni"), function(x) p_value(x))

@@

   # Fit model
      PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion + Predator:BodyRegion + Predator:Population + (1|ID), data=Predator)
      anova(PredatorAC)

   # Robust variance estimators (RVE). Mostly all consistent
             Predator_subset <- Predator %>% filter(!is.na(Population), !is.na(BodyRegion))
    robust_PredatorAC <- coef_test(PredatorAC, cluster = Predator_subset$ID, vcov="CR2")

  # Fit model for linear hypothesis tests
    Predator$PopBRInt <- interaction(Predator$Population,Predator$Predator, Predator$BodyRegion)
     ConspicDisplayCC2 <- lmer(dS ~ -1 + PopBRInt + (1|ID), data=Display_1)
     summary(ConspicDisplayCC2)

 # Contrasts hypothesis tests, but use RVE 
                 result2 <- Wald_test(ConspicDisplayCC2, constraints = constrain_pairwise(c(2:9)), vcov="CR2", tidy = TRUE)
    result2$p_val_bonfer <- sapply(p.adjust(result2$p_val, "bonferroni"), function(x) p_value(x))
# Posthoc tests
Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorAC2 <- lmer(sqrt_dL ~ PopBRInt + (1|ID), data=Predator)
summary(glht(PredatorAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                    "Hawaii.midflank - Kenya.midflank = 0", 
                                                    "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))
## dropping background from model (it is still averaged)
# anova gives us significance of fixed effects
# ranova tests random effects (note: report just LRT and df)
# need the SD of residuals and random effects from summary (just report random effects)
